%-------------------------
% Resume in Latex
% Author : Syed Ali Raza
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Syed Ali Raza} \\ \vspace{16pt}
    \small 085 209 9600 $|$ 
    Apt 2, 3 Dublin Road, Portlaoise $|$ 
    Permission: EU Stamp 4
\end{center}

\begin{center}
    \href{mailto:isyedaliraza@gmail.com}{\underline{isyedaliraza@gmail.com}} $|$ 
    \href{https://linkedin.com/in/isyedaliraza}{\underline{linkedin.com/in/isyedaliraza}} $|$
    \href{https://github.com/isyedaliraza}{\underline{github.com/isyedaliraza}}
\end{center}

%-----------Summary-----------
\section{Summary}
I'm a Software Engineer with over 5 years of experience in Full-stack development. I have worked with a variety of technologies like Flutter, React, Node.js, Django, Odoo, WordPress, Unity etc. I am a quick learner and love to learn new things. I always look for ways to improve my skills and build better software.

%-----------EMPLOYMENT HISTORY-----------
\section{Employment History}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{2020 -- 2024}
      {Business and Digital Technology Center -- Baramej®}{Muscat, OM}
      \resumeItemListStart
        \resumeItem{Implemented 3D data center infrastructure management system. Integrated IoT devices and third-party systems like PBX for SMS and Phone alerts.}
        \resumeItem{Developed a middleware insurance platform in Python and JavaScript, linking Omantel and Ooredoo with third-party insurance brokers.}
        \resumeItem{Developed metaverse identity for Ministry of Transport Communications and Information Technology using Unity.}
        \resumeItem{Developed and published a number of applications with features such as OAuth, payment integration, google maps integration, order management, booking management etc.}
        \resumeItem{Designed and developed REST APIs using Django, Flask, Node.js, Firebase Cloud Functions, and Laravel.}
        \resumeItem{Conducted training and knowledge transfer sessions.}
        \resumeItem{Managed administration related tasks such as processing sales and purchase invoices, communicating with customers via phone \& email, filing \& scanning paperwork etc.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Full Stack Developer}{2018 -- 2020}
      {Tilal Al Sad Projects and Investment L.L.C}{Muscat, OM}
      \resumeItemListStart
        \resumeItem{Developed and maintained responsive websites using Wordpress and Drupal.}
        \resumeItem{Designed and developed intuitive UIs using React, Bootstrap, Tailwind CSS, and Figma enhancing user experience.}
        \resumeItem{Modernized legacy systems by porting vanilla PHP projects to Node.js, improving performance and maintainability.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Computer and Emerging Sciences}{Islamabad, PK}
      {Bachelor of Science -- Computer Science}{2013 -- 2017}
    \resumeSubheading
      {FG Degree College for Men}{Wah Cantt, PK}
      {Intermediate -- Pre-Engineering}{2011 -- 2013}
    \resumeSubheading
      {POF Model High School}{Wah Cantt, PK}
      {Matriculation}{2011 -- 2013}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, Dart, Swift, Java, C++, HTML/CSS, SQL, NoSQL, JSON, XML} \\
     \textbf{Frameworks}{: Flutter, React, Next.js, Odoo, Node.js, Django, Laravel, WordPress, Drupal, Bootstrap, Tailwind CSS} \\
     \textbf{Developer Tools}{: Git, GitHub, Jira, Slack, Docker, Google Cloud Platform, Neovim, VS Code, PyCharm, IntelliJ, Xcode, Android Studio}\\
     \textbf{Design Tools}{: Figma, Adobe XD, Adobe Photoshop, Adobe Illustrator, Photopea}
    }}
 \end{itemize}

%-----------INTERPERSONAL SKILLS-----------
\section{Interpersonal Skills}
\small
Learning, Problem-solving, Teamwork/ Collaboration, Self-motivation, Ability to work under pressure, Time management, Adaptability, Responsibility, Communication

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\small
Was awarded fully-funded ICT scholarship (Prime Minister's National ICT Scholarship Award) to pursue Bachelor's degree in Computer Science

%-----------PUBLICATIONS-----------
\section{Publications}
S. Nizami, A. Basharat, A. Shaukat, U. Hameed, S. A. Raza, A. Bekele, R. Giffen, and J. R. Green, “CEA: Clinical Event Annotator mHealth Application for Real-time Patient Monitoring,” in the Proc. of 40th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC'18), Honolulu, HI, USA, July 17-21, 2018.


%-----------HOBBIES/ INTERESTS-----------
\section{Hobbies \& Interests}
Learning new things, Cybersecurity, Machine Learning, Gaming, Travelling, Food

%-----------REFERENCES-----------
\section{References}
Available upon request

%-------------------------------------------
\end{document}
